---
title: "Charley Creek Vegetation"
author: "Rebekah Stiling"
format: pdf
editor: visual
---

```{r}
#| warning: false
#| echo: false

# load relevant packages
library(tidyverse) #for wrangling and plotting
library(patchwork) # for multipanel plotting

#load data for publication
spcover_q<-read_csv("data/spcover.csv")


```

## Introduction

Vegetation percent cover surveys for this project were designed to estimate the quantities of beaver-preferred woody and herbaceous plant species along stream reaches.

## Methods

### Study area

These surveys occured in the Upper Green River Watershed, characterized by managed forest, limited human infrastructure, and no cell service. The Charley Creek Natural Area is DNR land ....

### Survey

Along eight transects perpendicular to each reach, we completed three 20-ft radius circular plots accounting for at least 10% of the site area. Within each reach, 8 circular plots were completed at 20 feet from water's edge, four of them on the right bank and four along the left bank. Beyond each plot located at 20, another was located along the same transect at 75 and 130ft. (FIGURE) Within each circle plot we estimated percent cover for all tree, shrub, and herbaceous plants species (excluding moss), noted observations of beaver and elk browse according to plant species, and recorded individual tree trunk size. Last, we estimated overall cover for each plot.

## Findings

```{r}
#| echo: false
obscount <-spcover_q  %>%  
  select(observation_date.only)   %>% 
  n_distinct() 
```

We completed  `r obscount`surveys in 

```{r}
#| echo: false
speciescount <-spcover_q |> 
  select(species_code)  |>
  n_distinct() 
```


Teams observed `r speciescount` different species in
